Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-07 paper.tex
Add orcid for both authors
Remove another typo

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric}
\usepackage{adjustbox}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Novel Desktop-as-a-Service}
%
\titlerunning{Challenges and Solutions of Developing and
	Implementing a Novel DaaS}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and
	Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
	Frankfurt University of Applied Sciences,\\
	Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
	\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
	Desktop-as-a-Service (DaaS) is a cloud service category with tremendous potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution, DESIGN, overcomes existing solutions' limitations and offers significant benefits. It can potentially revolutionize how we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

Compared to RDP, the protocol VNC offers fewer features in Guacamole since it does not support sound on its own. However, Guacamole supports sound using PulseAudio\footnote{On Linux operating systems, sound and microphone devices are accessed via sound servers like PulseAudio and PipeWire, which interact with the sound interface present in the kernel, e.g., Advanced Linux Sound Architecture (ALSA) or Open Sound System (OSS)} as a workaround solution. VNC also does not offer file transfer and access to external storage media. Still, as a workaround solution, Guacamole supports file transfer file transfer via the SSH File Transfer Protocol (SFTP), which is an extension of the Secure Shell protocol (SSH).

@@

% To describe the mission-critical performance aspects of the discussed system,
% we initially provide a brief overview of potential challenges
% by outlining bottlenecks and other relevant problem areas.
% This is done in the context of the underlying use case model of DaaS systems.
% Subsequently, we give a more comprehensive description
% of our specific design decisions and tailored solutions.
% Hence, every component from the core infrastructure
% to all backend services and user-facing elements,
% must meet individual and domain-specific requirements
% to contribute to the overall performance goals of the entire system.
% Thus, we outline key limiting factors that hinder performance,
% along with our experiences and the chosen mitigation strategies.
% Given the absence of a generalized measurement system,
% we ranked these factors based on their magnitude of impact,
% drawing from our experiences obtained during the project.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric}
\usepackage{adjustbox}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Novel Desktop-as-a-Service}
%
\titlerunning{Challenges and Solutions of Developing and
	Implementing a Novel DaaS}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and
	Johannes Bouché}
\author{Christian Baun\orcidID{0009-0004-9955-3752} \and
	Johannes Bouché\orcidID{0009-0009-8003-4019}
}

\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
	Frankfurt University of Applied Sciences,\\
	Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
	\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
	Desktop-as-a-Service (DaaS) is a cloud service category with tremendous potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution, DESIGN, overcomes existing solutions' limitations and offers significant benefits. It can potentially revolutionize how we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

Compared to RDP, the protocol VNC offers fewer features in Guacamole since it does not support sound on its own. However, Guacamole supports sound using PulseAudio\footnote{On Linux operating systems, sound and microphone devices are accessed via sound servers like PulseAudio and PipeWire, which interact with the sound interface present in the kernel, e.g., Advanced Linux Sound Architecture (ALSA) or Open Sound System (OSS)} as a workaround solution. VNC also does not offer file transfer and access to external storage media. Still, as a workaround solution, Guacamole supports file transfer via the SSH File Transfer Protocol (SFTP), which is an extension of the Secure Shell protocol (SSH).

@@
